Paper 2: Vitamin D

### 2018-04-13 doc/vitaminD.Rmd
added kidney measures to table 5.2 (changes over time)

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "MET",
           "VitaminD",
           "PTH",
           "UDBP",
           "udbpCr",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "dmStatus"),
  strata = c("VN"),
  data = m,
  factorVars = c("Sex", "Ethnicity", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "udbpCr"),
        quote = FALSE,
        noSpaces = TRUE) %>% 
  knitr::kable()

>>>>

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "MET",
           "VitaminD",
           "PTH",
           "ACR",
           "eGFR",
           "UDBP",
           "udbpCr",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "dmStatus"),
  strata = c("VN"),
  data = ds,
  factorVars = c("Sex", "Ethnicity", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "udbpCr",
                      "ACR"),
        quote = FALSE,
        noSpaces = TRUE) %>% 
  knitr::kable()
